---
title: 'Developing Data Products: Course Project Pitch Deck'
subtitle: 'Most Popular Baby Names Across Time in Hawaii' 
author: "Joe Barter"
date: "10/31/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Finding Some Fun Data 
After some research, the SSA's Popular Baby Names datasets looked like they would be an interesting dataset for this project.  

**Babies in a tropical islands paradise, what is not to love?**

Link to the site is https://www.ssa.gov/oact/babynames/limits.html 

A quick downloaded and scouting of the "State-specific data" led to focusing in on the data from Hawaii.  

This is what the data looks like: 
```{r, echo=FALSE, comment=''}
hiNames <- read.csv("HI.TXT", header = TRUE)
head(hiNames)
```

## Understanding the Data 
The data layout is pretty straightforward and allows for simple manipulation and quick data lookup.

```{r, echo=TRUE, comment=''}
str(hiNames)
```


## Making the Data Interactive
The next step was to create a quick user interface that would allow the user to browse the most popular names given:

* Number of **Top Names** to display
* **Gender** of the baby
* **Year** the baby was born

The heart of the server code utilizes the user's input to look up and render the the desired baby names.  


## Go and Play!
Use the link https://joebarter.shinyapps.io/PopularNamesAcrossTime/ to go and play with the Shiny application.  

Try the following:

* Check out how the popular names changed over time.  
* See if your name was popular in your birth year.  
* See if your friends and family members name was popular in their birth year. 
    + Parents
    + Siblings
    + Children
* Expand the list of names for more in depth analysis.

**Enjoy!**

